On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Fix another TODO

As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.

\Ethan{Combine the following two theorems}

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness.
\end{thm}
\begin{prf}
	The completeness follows by inspection.

@@

\begin{thm}
	\cref{proto:BlindBQP} is blind.
\end{thm}
\begin{prf}
	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{prf}

>>>>

As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.

@@
